---
title: "London's Crime Monitoring"
author: "mirzarashid abbasov | developing data products course | coursera | 06.JAN.2018"
output: html_document

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressMessages(library(leaflet))
suppressMessages(library(dplyr))
suppressMessages(library(sqldf))
suppressMessages(library(plotly))
suppressMessages(library(shiny))
```

#### Introduction
The following map represents London's crime statictics in 2016 year. Please click variables and analyze information.
```{r shinyApp, echo = FALSE}
# clean up workspance
rm(list = ls())

# setup work directory
setwd("/Users/mirzarashid.abbasov/repos/DevelopinDataProducts/week2/CrimeMonitor")

# load dataset
df <- read.csv("./data/df.csv")

# create lookups
crime.type              <- append(levels(df$Crime.type), 'all')
last.outcome.category   <- append(levels(df$Last.outcome.category), 'all')
month                   <- append(levels(df$Month), 'all')

dfSummarised <- sqldf("select 
                        t.month, 
                        t.'Crime.type', 
                        count(t.'Crime.type') 
                        from df t
                        group by t.month, t.'Crime.type'")
colnames(dfSummarised) <- c("month","crimeType","crimeTypeCount")  

# user interface
ui <- fluidPage(
        # titlePanel("London's crime monitoring"),
        sidebarLayout(
                sidebarPanel(
                        selectInput("month", label="Period", choices = month, selected = 1),
                        selectInput("crime.type", "Crime type", choices = crime.type, selected = 1),
                        checkboxInput("cluster", "Cluster option"),
                        checkboxInput("legend", "Popup option"),
                        br(),
                        br(),
                        br(),
                        br(),
                        br(),
                        br(),
                        br()
                ),
        mainPanel(
                leafletOutput("mymap"),
                plotlyOutput("myplot", width = "99%", height = 200)
                )
        )
)

# server side        
server <- function(input, output, session) {
        output$mymap <- renderLeaflet({
        set.seed(2018-01-06)
        dfFiltered <- df
                        
        if(input$month =='all')
                {
                        if(input$crime.type == 'all') {} 
                        else {dfFiltered <- filter(df, Crime.type == input$crime.type)}
                }
        else  
                        
                {
                        if(input$crime.type == 'all') {dfFiltered <- filter(df, Month == input$month)}
                        else {dfFiltered <- filter(df, Month == input$month & Crime.type == input$crime.type)}
                }
          
        myMap <- leaflet() %>% addTiles()
          
        
          if (input$legend == FALSE) 
                {
                        if (input$cluster == FALSE) {myMap <- myMap %>% addMarkers(dfFiltered$Longitude, dfFiltered$Latitude)}
                        else {myMap <- myMap %>% addMarkers(dfFiltered$Longitude, dfFiltered$Latitude, 
                                                 clusterOptions = markerClusterOptions())}
                }
          else 
                {
                        if (input$cluster == FALSE) {myMap <- myMap %>% addMarkers(dfFiltered$Longitude, dfFiltered$Latitude, 
                                                                        popup = dfFiltered$Last.outcome.category,
                                                                        label = dfFiltered$Crime.ID)}
                        else {myMap <- myMap %>% addMarkers(dfFiltered$Longitude, dfFiltered$Latitude, 
                                                 popup = dfFiltered$Last.outcome.category,
                                                 label = dfFiltered$Crime.ID,
                                                 clusterOptions = markerClusterOptions())}
          }  
        })
                
        output$myplot <- renderPlotly({
                
                m <- list(
                        l = 50,
                        r = 50,
                        b = 50,
                        t = 50,
                        pad = 4
                        )   
                
                if(input$crime.type == 'all') {} 
                else  {dfSummarised <- filter(dfSummarised, crimeType == input$crime.type)}
          
                p <- plot_ly(source = "source") %>% 
                        add_lines(data = dfSummarised, x = ~month, y = ~crimeTypeCount, 
                        color = ~crimeType, 
                        mode = "lines", line = list(width = 2))

                p <- p %>%
                        layout(title = paste("Trend for '", input$crime.type, "' during 2016"),
                        autosize = F, 
                        margin = m,
                        width = 550, height = 250,
                        yaxis = list(title = "crime type count")
                        )
                p
          
        })
}
        
shinyApp(ui, server, options = list(height = 700))        

```

#### Synopsis
The goal of the project is:

* create a web page using **R Markdown** that features a map created with **Leaflet**.
* host your webpage on either GitHub Pages, RPubs, or NeoCities.

#### Project's Dataset
This project use the [Data sourse:](https://data.police.uk/data/) These CSV files provide street-level crime, outcome, and stop and search information, broken down by police force an 2016 by City of London police.

***
######Mirzarashid Abbasov, almaty, 2018